Physics-based protein structure prediction and design using the confinement method

### 2013-01-11 Paper/paper.tex

In computational structural biology there are numerous cases where the free energy difference
between two well defined 
states plays an important role. Examples range from small to large conformational changes of proteins due to
ligand binding, change of pH or other conditions \cite{Meirovitch2007}, \cite{Chipot2007}, \cite{Jorgensen2004}. 
Free energy also plays an important role in the case of protein
folding. The ground breaking work of Christian B. Anfinsen and coworkers showed that the native
structures of small globular proteins have a unique, thermodynamically stable native structure with
their conformation at the global free energy minimum \cite{Anfinsen1973}. Regardless of the starting
point or even after unfolding 
it by changing different condition most proteins will go back to the native state after
reinstituting native like conditions. Often, the changes in free energy between different
conformations is small, but nonetheless crucial in favoring the native state
 since defects in protein folding may be
the molecular cause of a range of human genetic disorders. For example a misfolded protein known as
a
prion can misfold correctly folded proteins when entering a healthy organism.
\Alberto{I'm not sure I understand this here} \Arijit{Thus, Free energy can also act as a scale to identify between the misfolded and the native state of
the protein.} These facts further give free energy a special importance in structural biology.

However, the theoretical calculation of conformational free energy change becomes difficult if the
states of interest are very different \cite{Meirovitch2007}. In such scenario timescales involved in
such conformational transitions may
be beyond the sampling ability of classical molecular dynamics simulation.  Generally, in order to
calculate the free energy a pathway or reaction coordinate is needed with several intermediate structures.
Methods like umbrella sampling \cite{Torrie1977}, thermodynamic integration \cite{Tironi1994} along with classical MD can suffer from
overlap problem and require a large computational effort. The idea of a reaction coordinate became
even more
complicated in the case of protein folding.  As the free energy landscape for protein folding 
is rough \cite{Dill1997}, \cite{Dill2008}, the molecule 
can get trapped in an energy well during conformational sampling. Even with 
advanced methods like replica exchange molecular dynamics, the three dimensional structure may be
trapped in a local minima for a considerable time, giving rise to nonconverged distributions where
misfolded states might be selected as native like
% (give the example of human pin1ww domain from Benout Roux and Klaus Schultan).

The calculation of free energy has been successfully attempted by a number of groups \cite{Meirovitch2007}, 
\cite{Ytreberg2006} - \cite{Zheng2008}. In recent years methods like the Reference system method \cite{Ytreberg2006}, 
Decativated Morphing \cite{Park2008}, Orthogonal Space Random Work \cite{Zheng2008} or the Confinement 
Method \cite{Tyka2006}, \cite{Cecchini2009} to name a few have been used to calculate free energy
differences.
In this work we have applied the confinement method which was originally devoled by Tyka et. al. \cite{Tyka2006} and
Cecchini et. al. \cite{Cecchini2009}. This method relies on the fact that the free energy difference is a state function and 
thus it is independent of the sampling path. This approach uses a thermodynamic cycle where first, non-harmonic degrees of
freedom are removed by applying a series of restraints to the system. Then the free energy of the
remaining harmonic system is obtained using a normal mode calculation and combined with the
non-harmonic part to give the total absolute free energy.  Previously, this method was applied to
calculate the conformational free energy of a 16 amino acid residue peptide, known as BHP.  We have
first reproduced that known result. Then we have applied this method to larger proteins for the
first time. The free energy difference of pairs of conformations in proteins with similar sequence but completely
different fold was calculated. \Alberto{i made this part too long, have to summarize here and define
better inside text?-->} Encouraged by the result, we applied the method to help tackle the
problem of protein conformation ranking. We did this by selecting different targets from the
Critical Assessment of Structure Prediction (CASP) event. In this event, different research groups
try to find the 3D structure of a protein given a sequence in a blind way using their methodologies. Upon comparing
with the real structure it is often seen that several groups are able to generate better structures
than the ones they submit, but are not able to identify them. This is known as the ranking problem,
and this method is able to correctly rank structures in the majority of cases we have tried.
 Finally, we have been exploring the ability of working on a per residue basis to identify which
 residues are the major players in the stabilization/destabilization of a pair of conformations. Our
 initial experience makes us thinkg that this method might be helpful in identifying key residues
 for protein design.

@@

To avoid this potential problem, we instead computed the relative free energy of two different
structural models for each sequence. One model is based on the GA structure and the other on the GB
structure (see Supporting Information for details on the modeling procedure). This is a much more
realistic test of the confinement method's ability to accurately calculate relative free energies.

The results of these calculations are presented in Figure~\ref{fig:orban}. The confinement method
identifies the correct structure for all five sequences. One of the hypothesis for fold switching
of chamelon sequence is that the structural transitions require states with diminished stability.
It is widely believed that if the free energy of the native state and the alternative state is within
 a range of $-5 Kcal/Mol$ then  it can quickly change fold when the stability of the native state 
decreases. The stability of the native state can decrease for a number reason ranging from chemical 
modification, breaking of disulphide bonds or mutations as in this case. The free energy differences, that
came out from our calculation ranges from
around 2.9 to 5.7 kcal/mol, which is consistent with the above hypothesis \cite{He2008}, \cite{{Alexander2009}}.

\subsection{Per residue free energy calculation can identify the mechanistic detail behind conformational pereference 
of a particular residue}

We decomposed the calculated free energy into per residue decomposition as described in the methods
section. This helps us to
identify important residues that stabilize a particular conformation. 
\Alberto{This is not Reader Friendly at all. we do not have to describe every little detail. I would
    rather have a table where we have the pairing and the reason for favoring one structure or the
    other. In the main text I would say that the main reason for preferences of one fold or another
    has to do with the relative solvent exposure of the residue in one conformation or another, or
    the possibility of stablishing hydrogen/salt bridges in one conformation. This would be my
preference, ditching everything below until the next section. What do you think?}
In this direction, we first calculate the per residue free energy for the GA95 and GB95 sequences. Similar to the total 
free energy for each sequence, we calculate the free energy difference between $4 \beta + \alpha$ and $3 \alpha$ structure for each 
residue. The free energy, $\Delta \Delta G (4 \beta + \alpha$ - $3 \alpha)$ is plotted in Figure~\ref{fig:orban_full}(F). 
In this plot, the negative peak indicate the residue will stabilize the $4 \beta + \alpha$ conformation of a particular
residue and the positive peak will stabilize the $3 \alpha$ structure. As, the differences of amino acid 
residues are only at 3 position, there are some common features of residues in both GA95 and GB95 sequences in both 
$3 \alpha$ and $4 \beta + \alpha$ conformation. They are reported in Figure~\ref{fig:orban_full} 
and Table~\ref{table:orban_perresidue}. Before, we further go into that detail, it is important to note that 
experimental observations classified the protein into two parts: Amino acids 9-51 are fully structured in both
the folds, where as residues 1-8 and 52-56 are unstructured in $3 \alpha$, but form $\beta$ strand in $4 \beta + \alpha$ structure.
Most of the amino acid residues in the region 1-9 favor $4 \beta + \alpha$ structure as can be seen from the plot 
Figure~\ref{fig:orban_full}(F). Here, we try to explain some of the largest peak in that plot. The residues Leu-5 and 
Leu-7 favor $4 \beta + \alpha$ structure as these hydrophobic residues are oriented towards the protein hydrophobic 
core, whereas in $3 \alpha$ structure they are exposed to the solvent (Figure~\ref{fig:orban_full}(A)). One can argue that 
hydrophilic residues in these positions can stabilize the $3 \alpha$ conformation.
The next big peak is located at position 11. A close observation of the sidechain orientation of residue Gln at position 11 reveal that it
is exposed to the protein surface in both the conformation, but in $3 \alpha$ structure it has an additional H-bond with Glu-15 which gives
it more stability compared to the $4 \beta + \alpha$ structure (Figure~\ref{fig:orban_full}(B)). The peak 
at position 14 is due to the hydrophilic Glu, which is completely
exposed to the solvent in $4 \beta + \alpha$ conformation as shown in
(Figure~\ref{fig:orban_full}(E)), but is only partially exposed 
to the solvent in $3 \alpha$ form. 
This is the reason why Glu at position 14 stabilize $4 \beta + \alpha$ conformation. Another high peak is at position 26, which indicate
that the residue in that position stabilizes $4 \beta + \alpha$ conformation. Again, the hydrophobic amino acid residue, Ala at position 26
is oriented towards the hydrophobic core of the protein in $4 \beta + \alpha$ conformation , whereas it is exposed towards the protein surface 
in $3 \alpha$ structure (Figure~\ref{fig:orban_full}(C)). Similar situations arise for residues at position 54 and 56. 
These residues are in the region, where $4 \beta + \alpha$ form is fully structured and $3 \alpha$ form is unstructured. 
As shown in Figure~\ref{fig:orban_full}(D), the sidechain of hydrophobic Val-54 is oriented towards the hydrophobic core in 
$4 \beta + \alpha$ conformation and thus have hydrophobic interactions with other residues in this conformation.
On the other hand, in $3 \alpha$ it is exposed to the solvent. The reverse happens for the residue at position 56.
Here the hydrophilic residue Glu is partially or not at all exposed to the protein surface in $4 \beta + \alpha$ but fully exposed 
to the solvent in $3 \alpha$ conformation (Figure~\ref{fig:orban_full}(G)). This is the reason, why one can see a positive peak for position 56. 
Similarly, hydrophobic Ile-49 in $4 \beta + \alpha$ conformation is exposed to protein surface and solvent, whereas as shown in 
Figure~\ref{fig:orban_full}(H)$3 \alpha$ conformation 
it has hydrophobic interaction with other hydrophobic residues in protein core.   
Now, let us discuss the differences of $3 \alpha$ and $4 \beta + \alpha$ fold due to specific difference of mutated amino acid 
residues in GA and GB sequence. The differences are in positions 20, 30 and 45. While GA95 has Leu-20-Ile-30-Leu-45, GB95 sequence 
has Ala-20-Phe-30-Tyr-45 at those position. One can find that the peak at position 49 stabilizes the GA sequence more than that of GB
sequence. In $3 \alpha$ fold, Ile-49 has hydrophobic interactions with Leu-20 and Ile-30 with GA sequence, whereas with GB sequence it 
has such interactions with smaller Ala-20 and Phe-30 residues (Figure~\ref{fig:orban_full}(I). In $3 \alpha$, with GB sequence, Phe-30 
being a larger group can not be completely accomodated in the hydrophobic core(Figure~\ref{fig:orban_full}(J)) and therefore, 
partially exposed to the protein surface. There is a very interesting difference for residue at position 45 as well. In GB95 sequence
and $4 \beta + \alpha$ fold there is H-bonding between Tyr-45 and Asp-47 (Figure~\ref{fig:orban_full}(K)), which is absent in the
$3 \alpha$ conformation. On the other hand with GA conformation, this H-bond is absent for both the conformation as there is a Leu at position
45. Although, one can not find much difference between $4 \beta + \alpha$ and $3 \alpha$ conformation
for position 20 for both GA95 and GB95 sequence. There are significant difference for the residues at position 30 and 45.  
These residues have some long term effects as well. As already explained, residue Ile-49 has much more hydrophic interactions with residues
at position 20 and 30 in GA sequence, which is less in GB sequence. There are difference for Asp-47 as well. With $3 \alpha$ conformation 
and GA95 sequence, Asp-47 has H-bonding with Lys-50, which is absent in the other conformation.

\begin{table}
\begin{center}
\caption{Analysis of per residue free energy decomposition of GA95 and GB95 sequence reveal that certain residues prefer
either $3 \alpha$  or $4 \beta + \alpha$ structure. These observations and the reason behind such conformational preferences are listed in this
table.}
\label{table:orban_perresidue}
\begin{tabular}{| l | l | l |}
\hline
    Observation                                & $3 \alpha$ structure           &    $4 \beta + \alpha$ structure                       \\ \hline
    Leu-5 and Leu-7 favor                      & hydrophobic residues are       & oriented towards the                                  \\ 
    $4 \beta + \alpha$                         & exposed to the solvent         & hydrophobic core                                      \\ \hline
    Gln-11 favors $3 \alpha$                   & Gln-11 has H-bond with Glu-15  & no such H-bond                                        \\ \hline
    Glu-14 favors $4 \beta + \alpha$           & hydrophilic residue partially  & completely exposed                                    \\       
                                               & exposed to the solvent         & to the solvent                                        \\ \hline        
    Ala-26 favors  $4 \beta + \alpha$          & hydrophobic residue oriented   & oriented towards the                                   \\ 
                                               & towards surface                & hydrophobic core                                       \\ \hline
    Ile-49 favors $3 \alpha$                   & hydrophobic interaction        & exposed to the                                          \\
                                               & inside the protein             & solvent                                                \\ \hline 
    Val-54 favors $4 \beta + \alpha$           & hydrophobic residue exposed    & hydrophobic interaction                                \\
                                               & to the solvent                 & inside the protein                                      \\ \hline
    Glu-56 favors $3 \alpha$                   & hydrophilic residue partially  & completely exposed                                    \\
                                               & exposed to the solvent         & to the solvent                                        \\ \hline
    Phe-30 in GB sequence                      & exposed to the solvent         & oriented towards the                                  \\
    favors $4 \beta + \alpha$                  & in protein surface             & hydrophobic core                                      \\ \hline   
    Tyr-45 in GB Sequence                      & No H-bonding                   & H-bond with Asp-47                                    \\  
    favors $4 \beta + \alpha$                  &                                &                                                       \\ \hline
    Asp-47 in GA sequence                      & H-bond with Lys-50             & No H-bond, No Tyr-45                                  \\  
    favors $3 \alpha$                                 &                         & in GA sequence                                         \\ \hline
\end{tabular}
\end{center}
\end{table}

\begin{figure}
\includegraphics[width=3.5 in,height=4 in]{orban.pdf}
\label{fig:orban}
\caption{The confinement method correctly predicts the structural preferences of six chameleon
sequences. (A) The six sequences used in this study. (B) Each sequence adopts either a Protein
G-like fold (denoted GB) or a three-helix bundle fold (denoted GA). The relative free energies of
the two folds are reported for each sequence.}
\end{figure}

\begin{figure}
\includegraphics[width=6.5 in,height=5.4 in]{orban_full.pdf}
\label{fig:orban_full}
\caption{Orientation of residues of different sidechains in $4 \beta + \alpha$ and $3 \alpha$ form
A. Orientation of Hydrophobic residues Leu-5 and Leu-7.
B. Gln-11 has H-bond with Glu-15 in $3 \alpha$, which is absent in $4 \beta + \alpha$
C. Hydrophobic Ala-26
D. Hydrophobic Val-54.
E. Hydrophilic Glu-14.
F. The plot of free energy difference for GA95 and GB95 sequence. Positive peak stabilize $3 \alpha$ form and negative peak 
stabilize $4 \beta + \alpha$. 
G. Hydrophilic Glu-56 .
H. Orientation of Hydrophic Ile-49.
I. With GA95 sequence, Ile-49 have hydrophic interaction with both Leu-20 and Ile-30.
J. Larger Phe-30 in GB sequence, move towards the protein surface in $4 \beta + \alpha$.
K. Tyr-45 form H-bond with Asp-47 in $4 \beta + \alpha$.}  
\end{figure}

%\begin{table}
%\caption{The confinement method correctly reproduces the structural preferences of a series of
%designed peptides. Each sequence adopts either a Protein G-like fold ($4 \beta + \alpha$) or forms a
%helix bundle ($3 \alpha$).}
%\label{table:orban}
%\begin{center}
%\begin{tabular}{l l l}\hline
%Changes in & $\Delta G$ (kcal/mol)    & $\Delta G$ (kcal/mol)     \\
 %Sequences & ($3 \alpha$ fold)        & ($4 \beta + \alpha$ fold) \\ \hline
%GA95       & $0.000$                  & $2.901 \pm 0.475$         \\
%GB95       & $4.365 \pm 0.460$        & $0.000$                   \\
%GA88       & $0.000$                  & $ 3.941 \pm 0.517$        \\
%GB88       & $5.576 \pm 0.464$        & $0.000$                   \\
%GA98       &  &                           \\ \hline
%GB98       &                          &                           \\ \hline
%\end{tabular}
%\end{center}
%\end{table}

@@

This method is particularly well suited to pick out the native/native like structure from misfolded or decoys. We have
tested this using different models from CASP (critical assessment of structure
prediction). CASP is a blind test in which different groups world wide apply their
methods to predict the 3D structure of proteins given their sequence. This is done with a strict 3
week limit on each target (3 day for servers) and each group is allowed to submit 5 possible
structures (ranked from best to worst). In our role as assessors during the CASP8 and CASP9 \cite{MacCallum2011}
competition we observed no correlation at all between the ordering of structures submited by the
groups and the real ranking compared to an experimental model \cite{Kryshtafovych2011}. The
consequences of this goes beyond
those five structures; the deeper meaning is that groups producing ensembles of structures are
generating structures that are better than the ones they submit, but they do not know about it. In
fact, when querrying different groups after the results were known, most groups agree that this is
the case. Beyond the CASP problem, this reflects on the modelers ability to correctly rank order
models in many different environments, such as structures for drug design leads or designing more
stable proteins or peptide mimetics such as peptoids. One of the main culprits of this lack of
accuracy is the fact that ranking is often done via a potential energy function, which in many cases
lacks an entropy component. Other initiatives including knowledge based potentials do use some sort
of free energy to rank order, but its accuracy is not enough. Our method provides a physics based
solution to this problem. We have tried two experiments centered on CASP. First we tried to rank
order some structures from the previous CASP9 experiment. We have tested different options for that purpose.
First, we rank order submitions from same group and then from different groups. Our second test was 
to check whether this method can do better quality assessment/metaprediction than the best group in that catagory in CASP9. 
In both methods, our ranking is determined as a free energy measure,
and it is compared with the ranking given by a geometrical comparison between native and submitted
models called GDT\_TS (Global distance test score \cite{Zemla2003}). 
GDT\_TS represents the average percentage of residues that are in close proximity in two
structures optimally superimposed using four different distance cutoffs (1, 2, 4 and 8 Å).

>>>>

In computational structural biology there are numerous cases where the free energy difference
between two well defined 
states plays an important role. Examples range from small to large conformational changes of proteins due to
ligand binding, change of pH or other conditions \cite{Meirovitch2007}, \cite{Chipot2007}, \cite{Jorgensen2004}. 
Free energy also plays an important role in the case of protein
folding. Ground breaking work of Christian B. Anfinsen and coworkers showed that the native
structures of small globular proteins have a unique, thermodynamically stable native structure with
their conformation at the global free energy minimum \cite{Anfinsen1973}. Regardless of the starting
point or even after unfolding 
it by changing different condition most proteins will go back to the native state after
reinstituting native like conditions. Often, the changes in free energy between different
conformations is small, but nonetheless crucial in favoring the native state
 since defects in protein folding may be the molecular cause of a range of human genetic disorders.
 For example a misfolded protein known as a
prion can misfold correctly folded proteins when entering a healthy organism. Thus it is important for 
protein to have its native structure. As protein native structure stays in the global free energy minimum, 
\Arijit{free energy can be used as a scale for accurate identification of misfolded state from the protein native state.}
\Alberto{I'm not sure I understand this here} 
These facts further give free energy a special importance in structural biology.

However, the theoretical calculation of conformational free energy change becomes difficult if the
states of interest are very different \cite{Meirovitch2007}. In such scenario timescales involved in
such conformational transitions may
be beyond the sampling ability of classical molecular dynamics simulation.  Generally, in order to
calculate the free energy a pathway or reaction coordinate is needed with several intermediate structures.
Methods like umbrella sampling \cite{Torrie1977}, thermodynamic integration \cite{Tironi1994} along with classical MD can suffer from
overlap problem and requires a larger computational effort. The idea of a reaction coordinate became
even more
complicated in the case of protein folding.  As free energy landscape for protein folding 
is rough \cite{Dill1997}, \cite{Dill2008}, the molecule 
can get trapped in an energy well during conformational sampling. Even with 
advanced methods like replica exchange molecular dynamics, the three dimensional structure may be
trapped in a local minima for a considerable time, giving rise to nonconverged distributions where
misfolded states might be selected as native like
% (give the example of human pin1ww domain from Benout Roux and Klaus Schultan).

The calculation of free energy have been successfully attempted by a number of groups \cite{Meirovitch2007}, 
\cite{Ytreberg2006} - \cite{Zheng2008}. In recent years methods like the Reference system method \cite{Ytreberg2006}, 
Decativated Morphing \cite{Park2008}, Orthogonal Space Random Work \cite{Zheng2008} or the Confinement 
Method \cite{Tyka2006}, \cite{Cecchini2009} to name a few have been used to calculate free energy
differences.
In this work we have applied the confinement method which was originally devoled by Tyka et. al. \cite{Tyka2006} and
Cecchini et. al. \cite{Cecchini2009}. This method relies on the fact that the free energy difference is a state function and 
thus it is independent of the sampling path. This approach uses a thermodynamic cycle where first, non-harmonic degrees of
freedom are removed by applying a series of restraints to the system. Then the free energy of the
remaining harmonic system is obtained using a normal mode calculation and combined with the
non-harmonic part to give the total absolute free energy.  Previously, this method was applied to
calculate the conformational free energy of a 16 amino acid residue peptide, known as BHP.  We have
first reproduced that known result. Next we have applied this method to larger proteins for the
first time. The free energy difference of pairs of conformations in proteins with similar sequence but completely
different fold was calculated. \Alberto{i made this part too long, have to summarize here and define
better inside text?-->} Encouraged by the result, we applied the method to help tackle the
problem of protein conformation ranking. We did this by selecting different targets from the
Critical Assessment of Structure Prediction (CASP) event. In this event, different research groups
try to find the 3D structure of a protein given a sequence in a blind way using their methodologies. Upon comparing
with the real structure it is often seen that several groups are able to generate better structures
than the ones they submit, but are not able to identify them. This is known as the ranking problem,
and this method is able to correctly rank structures in the majority of cases we have tried.
 Finally, we have been exploring the ability of working on a per residue basis to identify which
 residues are the major players in the stabilization/destabilization of a pair of conformations. Our
 initial experience makes us thinkg that this method might be helpful in identifying key residues
 for protein design.

@@

To avoid this potential problem, we instead computed relative free energy of two different
structural models for each sequence. One model is based on the GA structure and the other on the GB
structure (see Supporting Information for details on the modeling procedure). This is a much more
realistic test of the confinement method's ability to accurately calculate relative free energies.

The results of these calculations are presented in Figure~\ref{fig:orban}. Confinement method
identifies the correct structure for all five sequences. One of the hypothesis for fold switching
of chamelon sequence is that the structural transitions require states with diminished stability.
It is widely believed that if the free energy of the native state and the alternative state is within
 a range of $5 Kcal/Mol$ then it can quickly change fold when the stability of the native state 
decreases. The stability of the native state can decrease for a number reason ranging from chemical 
modification, breaking of disulphide bonds or mutations as in this case. The free energy differences, that
came out from our calculation ranges from
around 3.5 to 5.0 kcal/mol, which is consistent with the above hypothesis \cite{He2008}, \cite{{Alexander2009}}.

\subsection{The per residue free energy calculation can identify the mechanistic detail behind conformational pereference 
of a particular residue}

We decomposed the calculated free energy into per residue decomposition as described in the method
section. This helps us to identify important residues that stabilize a particular conformation. 
In this direction, we first calculate the per residue free energy for the GA95 and GB95 sequences. 
The per residue free energy, $\Delta \Delta G ((4 \beta + \alpha$) - ($3 \alpha))$ is plotted in Figure~\ref{fig:orban_full}(F).
In this plot, the negative peak indicate the residue will stabilize the $4 \beta + \alpha$ conformation of a particular
residue and the positive peak will stabilize the $3 \alpha$ structure. As, the differences of amino acid
residues are only at 3 position, there are some common features of residues in both GA95 and GB95 sequences in both
$3 \alpha$ and $4 \beta + \alpha$ conformation. Role of some important residues in stabilizing either 
$4 \beta + \alpha$ or $3 \alpha$ conformation and possible reason for such conformational preferences are discussed in 
details in Figure~\ref{fig:orban_full} and Table~\ref{table:orban_perresidue}. It is important to note that
experimental observations classified the protein into two parts: Amino acids 9-51 are fully structured in both
the folds, where as residues 1-8 and 52-56 are unstructured in $3 \alpha$, but form $\beta$ strand in $4 \beta + \alpha$ structure.
Most of the amino acid residues in the region 1-9 favor $4 \beta + \alpha$ structure as can be seen from the plot
Figure~\ref{fig:orban_full}(F). Interestingly, we can explain most of the big peak in this plot. They are presented 
in Figure~\ref{fig:orban_full} and Table~\ref{table:orban_perresidue}. Here, we explain only one case. The first big peak
appears at position 7. Here, the hydrophobic Leu-7 stabilizes the $4 \beta + \alpha$ conformation as its sidechain is oriented 
towards the protein hydrophobic core, whereas in $3 \alpha$ structure it exposed to the solvent (Figure~\ref{fig:orban_full}(A)).
Thus, if someone want to better design the $3 \alpha$ conformation of this protein, we propose to mutate Leu at this position
with some hydrophilic residue. Similarly, we found that the free energy differences arise in two conformation for various 
reasons ranging from hydrogen/salt bridge formation to relative solvent exposure of hydrophobic residues etc. They are 
listed in Figure~\ref{fig:orban_full} and Table~\ref{table:orban_perresidue}.

\Alberto{This is not Reader Friendly at all. we do not have to describe every little detail. I would
    rather have a table where we have the pairing and the reason for favoring one structure or the
    other. In the main text I would say that the main reason for preferences of one fold or another
    has to do with the relative solvent exposure of the residue in one conformation or another, or
    the possibility of stablishing hydrogen/salt bridges in one conformation. This would be my
preference, ditching everything below until the next section. What do you think?}

\Arijit{I have rewrite this part.There was a table. I made it better. I want to keep some discussion though if you agree.}

Now, let us discuss the differences of $3 \alpha$ and $4 \beta + \alpha$ fold due to specific difference of mutated amino acid 
residues in GA and GB sequence. The differences are in positions 20, 30 and 45. While GA95 has Leu-20-Ile-30-Leu-45, GB95 sequence 
has Ala-20-Phe-30-Tyr-45 at those position. One can find that the peak at position 49 stabilizes the GA sequence more than that of GB
sequence. In $3 \alpha$ fold, Ile-49 has hydrophobic interactions with Leu-20 and Ile-30 with GA sequence, whereas with GB sequence it 
has such interactions with smaller Ala-20 (Figure~\ref{fig:orban_full}(I). In $3 \alpha$, with GB sequence, Phe-30 
being a larger group can not be completely accomodated in the hydrophobic core(Figure~\ref{fig:orban_full}(I)) and therefore, 
partially exposed to the protein surface. There is a very interesting difference for residue at position 45 as well. In GB95 sequence
and $4 \beta + \alpha$ fold there is H-bonding between Tyr-45 and Asp-47 (Figure~\ref{fig:orban_full}(K)), which is absent in the
$3 \alpha$ conformation. On the other hand with GA conformation, this H-bond is absent for both the conformation as there is a Leu at position
45 (Figure~\ref{fig:orban_full}(J)). Although, one can not find much difference between $4 \beta + \alpha$ and $3 \alpha$ conformation
for position 20 for both GA95 and GB95 sequence. There are significant difference for the residues at position 30 and 45.  
These residues have some long term effects as well. As already explained, residue Ile-49 has much more hydrophic interactions with residues
at position 20 and 30 in GA sequence, which is less in GB sequence. There are difference for Asp-47 as well. With $3 \alpha$ conformation 
and GA95 sequence, Asp-47 has H-bonding with Lys-50, which is absent in the other conformation.

\begin{table}
\begin{center}
\caption{Analysis of per residue free energy decomposition of GA95 and GB95 sequence reveal that certain residues prefer
either $3 \alpha$  or $4 \beta + \alpha$ structure. These observations and the reason behind such conformational preferences are listed in this
table.}
\label{table:orban_perresidue}
\begin{tabular}{| l | l | l |}
\hline
    Information from per                                 & What is happening in           & What is happening in                      \\ 
    residue plot                                         & $3 \alpha$ conformation        & $4 \beta + \alpha$  conformation          \\ \hline
    Leu-7 favors                                         & hydrophobic residue is         & oriented towards the                      \\ 
    $4 \beta + \alpha$ (Figure~\ref{fig:orban_full}(A))  & exposed to the solvent         & hydrophobic core                          \\ \hline
    Gln-11 stabilizes $3 \alpha$                   & Gln-11 has H-bond                         & no such H-bond                           \\ 
    (Figure~\ref{fig:orban_full}(B))           &  with Glu-15                              &                                           \\ \hline 
    Glu-14 favors $4 \beta + \alpha$           & hydrophilic residue partially  & completely exposed                                    \\       
    (Figure~\ref{fig:orban_full}(E))           & exposed to the solvent         & to the solvent                                        \\ \hline        
    Ala-26 favors  $4 \beta + \alpha$          & hydrophobic residue            & oriented towards the                                   \\ 
     (Figure~\ref{fig:orban_full}(C))          & oriented towards surface       & hydrophobic core                                       \\ \hline
    Ile-49 favors $3 \alpha$                   & hydrophobic interaction        & sidechain exposed                                       \\
    (Figure~\ref{fig:orban_full}(H) and (I))   & inside the protein             & to the solvent                                          \\ \hline 
    Ile-49 favors GA more                      & more hydrophobic               &  unchanged                                              \\
    than GB                                    & interactions with residues     &                                                         \\ 
    (Figure~\ref{fig:orban_full}(H) and (I))  &  at 20, 30 in GA                &                                                         \\ \hline
    Val-54 favors $4 \beta + \alpha$           & hydrophobic residue            & hydrophobic interaction                                \\
    Figure~\ref{fig:orban_full}(D))             & exposed to the solvent        & inside the protein                                      \\ \hline
    Glu-56 favors $3 \alpha$                   & hydrophilic residue partially  & completely exposed                                    \\
    (Figure~\ref{fig:orban_full}(G))            & exposed to the solvent         & to the solvent                                        \\ \hline
    Phe-30 in GB sequence                      & exposed to the solvent         & oriented towards the                                  \\
    stabilizes $4 \beta + \alpha$                  & in protein surface             & hydrophobic core                                      \\ \hline   
    Tyr-45 in GB favors                      & No H-bonding                   & H-bond with Asp-47                                    \\  
    $4 \beta + \alpha$ (Figure~\ref{fig:orban_full}(K))&                 &                                                       \\ \hline
    Asp-47 in GA sequence                      & H-bond with Lys-50             & No H-bond, No Tyr-45                                  \\  
    favors $3 \alpha$                          &                         & in GA sequence                                         \\ \hline
\end{tabular}
\end{center}
\end{table}

\begin{figure}
\includegraphics[width=3.5 in,height=4 in]{orban.pdf}
\label{fig:orban}
\caption{Confinement method correctly predicts the structural preferences of six chameleon
sequences. (A) The six sequences used in this study. (B) Each sequence adopts either a Protein
G-like fold (denoted GB) or a three-helix bundle fold (denoted GA). The relative free energies of
the two folds are reported for each sequence.}
\end{figure}

\begin{figure}
\includegraphics[width=6.4 in,height=5.3 in]{orban_full.pdf}
\label{fig:orban_full}
\caption{Sidechain orientation of some important residues which stabilize/destabilize either of the $4 \beta + \alpha$ or $3 \alpha$ conformation.
The details are in Table~\ref{table:orban_perresidue} and the main text.  
A. Leu-7.
B. Gln-11 has H-bond with Glu-15 in $3 \alpha$, which is absent in $4 \beta + \alpha$
C. Ala-26
D. Val-54.
E. Glu-14.
F. plot of free energy difference for GA95 and GB95 sequence. Positive peak stabilize $3 \alpha$ form and negative peak 
stabilize $4 \beta + \alpha$. 
G. Glu-56 .
H. sidechain orientation of Hydrophic Ile-49, along with Leu-20 and Ile-30 with GA95 sequence
I. sidechain orientation of Hydrophic Ile-49, along with Ala-20 and Phe-30 with GB95 sequence
J. Tyr-45 forms H-bond with Asp-47 with GB95 sequence and $4 \beta + \alpha$ conformation
K. No H-bond possible between Leu-45 and Asp-47 with GB95 sequence and $4 \beta + \alpha$ conformation .}  
\end{figure}

%\begin{table}
%\caption{Confinement method correctly reproduces the structural preferences of a series of
%designed peptides. Each sequence adopts either a Protein G-like fold ($4 \beta + \alpha$) or forms a
%helix bundle ($3 \alpha$).}
%\label{table:orban}
%\begin{center}
%\begin{tabular}{l l l}\hline
%Changes in & $\Delta G$ (kcal/mol)    & $\Delta G$ (kcal/mol)     \\
 %Sequences & ($3 \alpha$ fold)        & ($4 \beta + \alpha$ fold) \\ \hline
%GA95       & $0.000$                  & $2.901 \pm 0.475$         \\
%GB95       & $4.365 \pm 0.460$        & $0.000$                   \\
%GA88       & $0.000$                  & $ 3.941 \pm 0.517$        \\
%GB88       & $5.576 \pm 0.464$        & $0.000$                   \\
%GA98       &  &                           \\ \hline
%GB98       &                          &                           \\ \hline
%\end{tabular}
%\end{center}
%\end{table}

@@

This method is particularly well suited to pick out the native/native like structure from misfolded or decoys. We have
tested this using different models from CASP (critical assessment of structure
prediction). CASP is a blind test in which different groups world wide apply their
methods to predict the 3D structure of proteins given their sequence. This is done with a strict 3
week limit on each target (3 day for servers) and each group is allowed to submit 5 possible
structures (ranked from best to worst). In our role as assessors during the CASP8 and CASP9 \cite{MacCallum2011}
competition we observed no correlation at all between the ordering of structures submited by the
groups and the real ranking compared to an experimental model \cite{Kryshtafovych2011}. The
consequences of this goes beyond
those five structures; the deeper meaning is that groups producing ensembles of structures are
generating structures that are better than the ones they submit, but they do not know about it. In
fact, when querrying different groups after the results were known, most groups agree that this is
the case. Beyond the CASP problem, this reflects on the modelers ability to correctly rank order
models in many different environments, such as structures for drug design leads or designing more
stable proteins or peptide mimetics such as peptoids. One of the main culprits of this lack of
accuracy is the fact that ranking is often done via a potential energy function, which in many cases
lacks an entropy component. Other initiatives including knowledge based potentials do use some sort
of free energy to rank order, but its accuracy is not enough. Our method provides a physics based
solution to this problem. We have tried two experiments centered on CASP. First we tried to rank
order some structures from the previous CASP9 experiment. We have tested different options for that purpose.
First, we rank order submitions from same group and then from different groups. Our second test was 
to check whether this method can do better quality assessment/metaprediction than the best group in that catagory in CASP9. 
In both methods, our ranking is determined as a free energy measure,
and it is compared with the ranking given by a geometrical comparison between native and submitted
models called GDT\_TS (Global distance test score \cite{Zemla2003}). 
GDT\_TS represents the average percentage of residues that are in close proximity in two
structures optimally superimposed using four different distance cutoffs (1, 2, 4 and 8 \AA).
